\documentclass[10pt,a4paper]{article}
\title{Selection Sort}
\date{}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
% For algorithms
\usepackage[linesnumbered,ruled,lined,boxed,commentsnumbered]{algorithm2e}

\usepackage{titling}

\setlength{\droptitle}{-10em} 

\begin{document}
\maketitle

\begin{algorithm}[H]
 \KwData{An array A[0 ... n-1] of size n}
 \KwResult{Sorted array A in non decreasing order i.e $A[0]<=A[1]<=...<=A[n-1]$ }
  \BlankLine
  \Begin {
  \For{$i \leftarrow 0$ to $n-2$} {
  	$min \leftarrow i$\;
  	\tcc{Find minimum element of sub-array A[i..n-1]}
  	\For{$j \leftarrow i+1$ to $n-1$} {
  		\If{$A[min] > A[j]$}{
  			$min \leftarrow j$\;
  		}
  		$j \leftarrow j+1$\; 
  	}
  	\BlankLine
  	\tcc{Swap A[i] and A[min]}
  	$tmp \leftarrow A[min]$\;
  	$A[min] \leftarrow A[i]$\;
  	$A[i] \leftarrow tmp$\;
  	\BlankLine
  	$i \leftarrow i+1$\;
 }
 }
 \caption{Selection Sort}
\end{algorithm}

\section{Proof of Correctness}
\subsection{Invariant}
At the beginning of each outer for loop, the sub array $A[0 \text{ .. } i-1]$ consists of the first $i$ smallest elements of the entire array A, in sorted order.

\subsection{Initialization}
Initially, $i = 0$ and hence the sub array $A[0 \text{ .. } i-1]$ is an empty list and consists of 0 
elements. As the list is empty, the invariant trivially holds.

\subsection{Maintenance}
The inner for loop runs from $j \leftarrow i+1$ through $n-1$. It is not too difficult to see that when the inner for loop terminates, the variable $min$ contains the index of the smallest element in the sub array $A[i \text{ .. } n-1]$. $A[min]$ is then swapped with $A[i]$, thereby giving us the first $i+1$ smallest elements in $A[0 \text{ .. } i]$, that too in sorted order. Incrementing $i$ then makes the invariant hold at the start of the next iteration.

\subsection{Termination}
The procedure terminates when $ i > n-2$. As $i$ is always incremented by 1, when the
outer while loop terminates $i$ will always be equal to $n-1$. According to the invariant, 
when $i = n-1$, the sub array $A[0 \text{ .. } n-2]$ must contain the first $(n-1)$ smallest elements
of A in sorted order. By elimination, $A[n-1]$ must now contain the $n^{th}$ smallest element.
In other words, the array $A$ is now sorted. $\blacksquare$

	
\end{document}
